---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# interchangeGUI

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/CCICB/interchangeGUI/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/CCICB/interchangeGUI/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

interchangeGUI makes it easy to convert common biological filetypes, increasing interoperability


## Installation

You can install the development version of interchangeGUI like so:

``` r
# install.packages('remotes')
remotes::install_github('CCICB/interchangeGUI')
```

## Example



```{r example}
library(interchangeGUI)
## basic example code
```


## Code of Conduct
Please note that the interchangeGUI project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
